### 2016-06-02 intro.tex
intro
adding tasks
adding interesting papers

Continuing on this point, it seems that the coins of~$\mathbf{B}_1$ (whatever their use) are intended to be kept secret from the adversary.  Thus, to the extent that it addresses real Bloom filters at all, the NY security notion only addresses applications in which the representation is created using secret coins.  But many real-world applications of Bloom filters have no secrets.  NY point to web proxies, which use Bloom filters to compactly represent the objects they store locally, as motivation for their work.  But real web proxies like Squid~\cite{xxx} do \emph{not} use secrets in their Bloom filters.  They use the basic Bloom filter with four hash functions, defined as follows: $h_1(x) = \mathrm{MD5}(x)[0,\ldots,31]$, $h_2(x)=\mathrm{MD5}(x)[32,\ldots,63]$, $h_3(x)=\mathrm{MD5}(x)[64,\ldots,95]$, and $h_4(x)=\mathrm{MD5}(x)[96,\ldots,127]$.  Likewise, there are no secrets in the Bloom filters used by Google's BigTable~\cite{xxx}, HBase~\cite{xxx}, \tsnote{make an impressive list.}  There are applications in which the proposed Bloom filter instantiations do use secretly keyed hash functions, e.g. $h_j(x) = (f(K_0,x) + j\cdot g(K_1,x))\bmod m$, where $j\in[1,k]$, $m$ is the number of bits in the array, and where $f,g$ are PRFs keyed by secrets $K_0,K_1$.  This particular ``encrypted Bloom filter'' instantiation was suggested for use in efficient linking of records across separate medical record databases~\cite{xxx}.  (It was subsequently shown not to be secure by Niedermeier et al.~\cite{xxx}, where a clever use of frequency analysis recovered the last names of patients given access only to the Bloom filter array.\tsnote{This shows that false-positive security and privacy (whatever it is) are orthogonal, since I'm pretty sure this ``encrypted'' bloom filter resists FPs.})  In any case, it is clear that the NY definition does not capture the most widely used applications of Bloom filters, e.g. CDN summary caches, P2P network routing algorithms, etc.

\tsnote{Could also point out that their positive results use constructions that have secret keys, and these are unlikely to be of any use in major applications like CDNs or P2P networks.  But maybe the horse is sufficiently beaten by now...}

@@

\heading{Related work. }
Niedermayer et al., breaking privacy of secret-hash-function Bloom filters.
Mitzenmacher and Vadhan.\tsnote{Might only be tangential.}

>>>>

Continuing on this point, it seems that the coins of~$\mathbf{B}_1$ (whatever their use) are intended to be kept secret from the adversary.  Thus, to the extent that it addresses real Bloom filters at all, the NY security notion only addresses applications in which the representation is created using secret coins.  But many real-world applications of Bloom filters have no secrets.  NY point to web proxies, which use Bloom filters to compactly represent the objects they store locally, as motivation for their work.  But real web proxies like Squid~\cite{xxx} do \emph{not} use secrets in their Bloom filters.  They use the basic Bloom filter with four hash functions, defined as follows: $h_1(x) = \mathrm{MD5}(x)[0,\ldots,31]$, $h_2(x)=\mathrm{MD5}(x)[32,\ldots,63]$, $h_3(x)=\mathrm{MD5}(x)[64,\ldots,95]$, and $h_4(x)=\mathrm{MD5}(x)[96,\ldots,127]$.  Likewise, there are no secrets in the Bloom filters used by Google's BigTable~\cite{xxx}, HBase~\cite{xxx}, \tsnote{make an impressive list.}  There are applications in which the proposed Bloom filter instantiations do use secretly keyed hash functions, e.g. $h_j(x) = (f(K_0,x) + j\cdot g(K_1,x))\bmod m$, where $j\in[1,k]$, $m$ is the number of bits in the array, and where $f,g$ are PRFs keyed by secrets $K_0,K_1$.  This particular ``encrypted Bloom filter'' instantiation was suggested for use in efficient linking of records across separate medical record databases~\cite{xxx}.  (It was subsequently shown not to be secure by Niedermeier et al.~\cite{xxx}, where a clever use of frequency analysis recovered the last names of patients given access only to the Bloom filter array.\tsnote{This shows that false-positive security and privacy (whatever it is) are orthogonal, since I'm pretty sure this ``encrypted'' bloom filter resists FPs.})  In any case, it is clear that the NY definition does not capture the most widely used applications of Bloom filters, e.g. CDN summary caches, P2P network routing algorithms, etc.
\tsnote{Could also point out that their positive results use constructions that have secret keys, and these are unlikely to be of any use in major applications like CDNs or P2P networks.  But maybe the horse is sufficiently beaten by now...}

%\tsnote{What about content-based routing, or whatever that field is calling itself now?  A Bloom filter seems likely to be used there, and you'd want privacy for at least the content-seeker.}

@@

\heading{Related work. }
\begin{itemize}
\item Niedermayer et al., breaking privacy of secret-hash-function Bloom filters.
\item Mitzenmacher and Vadhan.\tsnote{Might only be tangential.}
\item Gerbet, Kumar and Lauradoux, ``The power of evil choices in bloom filters''.  \tsnote{Looks like a real goldmine of related work!}
\item Nojima and Kadobayashi, ``Cryptographically Secure Bloom Filters''.
\item Kerschbaum , ``Public-Key Encrypted Bloom Filters with Applications to Supply Chain Integrity''.
\item S\"{a}rell\"{a} et al. ``BloomCasting: Security in Bloom Filter Based Multicast''.
\end{itemize}
